Title

### 2012-05-03 inc/external_forces/external_forces.tex
worked out some teething issues for import package
updated external_forces to use term 'int' rather than 'force'
fixed typo added internal linkage between Kflow and ExtForces

\section{Extension to Include External Forces}

General form of (possibly multiple) external force ($\vec{F}_{ext}$) contributions
\begin{equation}
  \frac{\partial}{\partial t} A^{-1}_{ij} = K^{flow}_{ij} + K^{force}_{ij} + \sum K^{ext}_{ij}
\end{equation}
in the basis
\begin{equation}
  U_{i} = \lbrace x, p_x, y, p_y, z, p_z \rbrace
\end{equation}
and
\begin{equation}
  K^{ext}_{ij} = \frac{1}{N} \iint U_i U_j \left [ \frac{\partial}{\partial \vec{p}} f(\vec{r}, \vec{p}; t) \right ] \cdot \vec{F}_{ext}\;d^{3}x\,d^{3}p
\end{equation}

>>>>

\section{Extension to Include External Forces} \label{sec:external_forces}

General form of (possibly multiple) external force ($\vec{F}_{ext}$) contributions
\begin{equation}
  \frac{\partial}{\partial t} A^{-1}_{ij} = K^{flow}_{ij} + K^{int}_{ij} + \sum K^{ext}_{ij}
\end{equation}
again in the basis defined in \ref{eq:coordinate_vector} is given by
\begin{equation}
  K^{ext}_{ij} = \frac{1}{N} \iint u_i u_j \left [ \frac{\partial}{\partial \vec{p}} f(\vec{r}, \vec{p}; t) \right ] \cdot \vec{F}_{ext}\;d^{3}x\,d^{3}p
\end{equation}
